---
title: "ioslides"
date: "14 October 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F,fig.width=3,fig.asp=.8,echo=F,warning=F,message=F)
source('ipf1dataget.R') #problem with filepaths either here or inside the script 20171011
```

## 010  Performance last 12m

```{r , echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
    cl1(dezo2d,dex='r1y',width='450px',height='450px')
```

## 020  Valuation trends over 23 years

High price -> high performance

```{r }
x2 <- xx020
x3 <- ggplot(x2[grepl('^ ',variable)],aes(date,value),color=variable)+
  geom_line(aes(color=variable),size=.5)+
  scale_y_log10()+ylab('£/m2 (logarithmic scale)')+ 
  guides(color=guide_legend(title="percentile")) + 
  xlab('') + theme(legend.position = "bottom")
ggplotly(x3)
```


## 030  Tipping point?

* All the outperformance had already occurred 1995-2001 - the rest is compounding  
* There followed a period of price convergence, as lower-valued regions 'caught up'
* We are now at almost exactly the same 'strain level' between percentiles 25 and 75

As of 2001 yearend the quartile 1 postcode was `r xx030a[,x1a1]`, valued at `r xx030a[,x1a2]` £/m2 and the quartile 3 postcode was `r xx030a[,x1b1]`, valued at `r xx030a[,x1b2]` £/m2

As of 2017Q3 the quartile 1 postcode was `r xx030a[,x2a1]`, valued at `r xx030a[,x2a2]` £/m2 and the quartile 3 postcode was `r xx030a[,x2a1]`, valued at `r xx030a[,x2a2]` £/m2

```{r }
x2 <- xx030b
x3 <- ggplot(x2[grepl('^75/25',variable)],aes(date,value)) + 
  geom_line(aes(color=variable),size=.7) + 
  ylab('relative £/m2, quartile 4/quartile 1') + 
  theme(legend.position="none")
ggplotly(x3)
```

## 040  Last 4 quarters: a mixed picture on price convergence/divergence 

```{r }
x3 <- xx040d
x4 <- ggplot(x3,aes(ppm2t,r1y,text=zo))+geom_point(size=.5) + 
  ylab('4 quarters return from 2016Q3') + 
  xlab('£/m2 2016Q3') + theme(legend.position = "bottom")
x4 %>% ggplotly(tooltip='text')
```

## 041  Last 4 quarters: London area price convergence

Affordability has driven buyers to the periphery.

```{r }
x3 <- xx041d
x4 <- ggplot(x3[grepl('^E--|^W--|^N--|^SE-|^SW-|^RM-|^SO-|^UB-|^CR-|^HA-',zo)],aes(ppm2t,r1y,text=zo,color=area))+
  geom_point(size=1) + 
  ylab('4 quarters return from 2016Q3') + 
  xlab('£/m2 at period start') + theme(legend.position = "bottom")
x4 %>% ggplotly(tooltip='text')
```
</br>

## 050  Risk attribution

* Only 6% of risk (variance of annual returns) is not captured by the first 3 national factors  

* A local factor model captures most of the remaining residual risk

```{r, fig.width=6, fig.asp=.8 }
x1 <- xx050d
x2 <- ggplot(x1,aes(x="",y=value,fill=variable)) + geom_col(width=1) 
x3 <- x2 +coord_polar("y",dir=-1)+theme_void()+ guides(fill=guide_legend(title="")) + ggtitle("Systematic Risk in Resi Returns","Attribution of Variance in PCA Factor Model")
x3
# ggplotly(x3) #nothing at all online about this and not works
```

## 060 repeat sales numbers

```{r }
  x1 <- ggplot(xx060d,aes(variable,value/1e6,fill=variable)) +
    geom_bar(stat='identity') +
    xlab('') +
    ylab('million') +
    theme(legend.position="none") +
  theme(axis.text.x=element_text(angle = 90, hjust = 0))
  ggplotly(x1)
```
